formula1: top 9 drivers

### 2023-01-10 inst/formula1_top9.Rmd
Fixes #91

```{r,hamiltonwetanddry,cache=TRUE}
details <- read.table("formula1_conditions.txt",header=TRUE)
alldrivers <- c("Ham_dry","Ham_wet",rownames(f2017)[-1])
(L2017 <- hyper2(pnames=alldrivers)) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	print(o)
	L2017 %<>% order_obs(o)
}  # for(i) loop closes
L2017
```

>>>>

```{r,hamiltonwetanddry,cache=TRUE}
details <- read.table("formula1_conditions.txt",header=TRUE)
alldrivers <- c("Ham_dry","Ham_wet",rownames(f2017)[-1])
(L2017 <- hyper2(pnames=alldrivers)) # uninformative
for(i in seq_len(ncol(f2017))){
	venue <- colnames(f2017)[i]
	conditions <- details[which(details$venue == venue),4]
	o <- f2017[,i]
	names(o) <- rownames(f2017)
	if(conditions == "wet"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_wet"
	} else if(conditions == "dry"){
	   names(o)[names(o) == "Hamilton"] <- "Ham_dry"
	} else {
	   stop("neither wet nor dry?")
	}
	print(o)
	L2017  <- L2017 + ordervec2supp(o) # NB zero  -> "Did not finish"
}  # for(i) loop closes
L2017
```
